---
title: "apogee_rosemount_summer_2017"
author: "Erin Gilbert"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    code_folding: hide
    toc: yes
    toc_float: True
    toc_depth: 4
    fig_retina: 2
    number_sections: False
    highlight: zenburn
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(DT)
require(raster)
require(rgdal)
require(EBImage)
require(rjson)
```


# SDS Rosemount
This RMarkdown generated principle components for data collected on the Apogee handheld 

Planting notes:
SDS Inoculated at planting
Substrate in seed packets

##Experimental Setup {.tabset}

### Plot Experimental Design
```{r loading_files_into_dataframe}


#setwd("/Volumes/CFANS/") 
directory<-"/Volumes//hirsch_lab/projects/soybean/sds_bsr/apogee/a8/raw"
files<-list.files(directory) #get all names in file

###Experiment info
experiment_info<-t(data.frame(strsplit(files, split="-")))
row.names(experiment_info)=NULL
#experiment_info<-experiment_info[,-ncol(experiment_info)]
colnames(experiment_info)<-unlist(strsplit(experiment_info[1,], split="_"))[seq(1,ncol(experiment_info)*2,2)]
#experiment_info<-experiment_info[,-ncol(experiment_info)]
experiment_info<-as.data.frame(apply(experiment_info, 2, function(x) unlist(strsplit(x,split="_")))[seq(2,nrow(experiment_info)*2,2),])
#experiment_info<-experiment_info[-1,]

# #Combining data
# apogee_transmission_readings<-read.table(paste(directory, files[1], sep=""), header = F, skip=3)
# 
# for(i in 2:length(files))
# {
#   temp<-read.table(paste(directory,files[i], sep=""), header=F, skip=3)
#   apogee_transmission_readings<-cbind(apogee_transmission_readings, temp[,2])
#  
# }
# 
# names(apogee_transmission_readings)<-c("Wavelength", paste(experiment_info$Plot, experiment_info$Leaf, sep="_"))
# 
# 
# 
# #clean up data
# apogee_transmission_readings<-subset(apogee_transmission_readings, Wavelength>400 & Wavelength<1200)
# #apogee_transmission_readings<-apogee_transmission_readings[,-unique(which(apogee_transmission_readings>150, arr.ind = T)[,2])[-1]]
# apogee_transmission_readings<-t(apogee_transmission_readings)[-1,]

apogee_transmission_readings<-read.csv("~/Desktop/apogee.csv")
apogee_transmission_readings_backup<-apogee_transmission_readings
#experiment_info<-experiment_info[which(experiment_info$Plot %in% as.data.frame(strsplit(paste(experiment_info$Plot, experiment_info$Leaf, sep="_"), split="_"), stringsAsFactors=F)[1,]),]
experiment_info$Leaf<-gsub('.TRM|1|2|3','',experiment_info$Leaf)
experiment_info_backup<-experiment_info



#experiment_info["means"]<-colMeans(apogee_transmission_readings[,-1])

unik<-!duplicated(experiment_info$Plot)
experiment_info_reduced<-experiment_info[unik,]
experiment_info_reduced<-experiment_info_reduced[,1:6]

datatable(experiment_info_reduced)

```

### Readings Log

```{r rsmnt_readings_info}

datatable(experiment_info)
```


##Principle components on leaves


###PCs All leaves by inoculation status {.tabset}
PLOTS SHOW PC1xPC2 and PC3&PC4 FOR EACH DAY 

Uninoculated = Blue | Inoculated= Orange


####MINNSOY
```{r rsmnt_pc_minnsoy_trt, fig.align='center'}
apogee_transmission_readings<-apogee_transmission_readings_backup
genotype=unique(experiment_info$Genotype)[1] ##change the number for the genotype you want
#unique(experiment_info$Genotype) = Minnsoy Noir    McCall  MN1606  Ag2107 MN1410 
for (plot_day in sort(as.numeric(as.character(unique(experiment_info$PictureDay)))))
{

apogee_transmission_readings_plot<-as.data.frame(apogee_transmission_readings[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype == genotype),])
if  (nrow(apogee_transmission_readings_plot)>1){ #if there is more than 1 reading
# curve_areas_means<-NULL
# for(i in 1:ncol(apogee_transmission_readings_means_plot))
# {
# curve_areas_means<-cbind(curve_areas_means, diff(apogee_transmission_readings_means_plot[,i])/diff(apogee_transmission_readings_means_plot_day[,1]))
# }

pca_plot_mean<-prcomp(apogee_transmission_readings_plot)


#par(mfrow=c(4,1))
# plots_for_plot_day<-sort(unique(unlist(strsplit(names(apogee_transmission_readings_means_plot_day)[grep(paste("_", plot_day, sep=""),names(apogee_transmission_readings_means_plot_day))], split = "_"))))[-1]

clr<-c("blue", "orange")
if(ncol(pca_plot_mean$x) >1) #if there was enough data to generate at least 2 PCs
{plot(pca_plot_mean$x[,1], pca_plot_mean$x[,2], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 1&2", genotype,"All Leaves per Plot Day", plot_day), xlab="PC1", ylab="PC2", pch=20)}
if(ncol(pca_plot_mean$x) >3) #if PC 3 and 4 are there
{plot(pca_plot_mean$x[,3], pca_plot_mean$x[,4], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 3&4", genotype,"All Leaves per Plot Day", plot_day), xlab="PC3", ylab="PC4", pch=20)}
#legend("bottomleft",legend=c("uninoc", "inoc"), col=c("orange", "blue"), pch=19)#colorbyinoculationstatus
}
}
```

####NOIR
```{r rsmnt_pc_noir_trt, fig.align='center'}
apogee_transmission_readings<-apogee_transmission_readings_backup
genotype=unique(experiment_info$Genotype)[2] ##change the number for the genotype you want
#unique(experiment_info$Genotype) = Minnsoy Noir    McCall  MN1606  Ag2107 MN1410 
for (plot_day in sort(as.numeric(as.character(unique(experiment_info$PictureDay)))))
{

apogee_transmission_readings_plot<-as.data.frame(apogee_transmission_readings[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype == genotype),])
if  (nrow(apogee_transmission_readings_plot)>1){ #if there is more than 1 reading
# curve_areas_means<-NULL
# for(i in 1:ncol(apogee_transmission_readings_means_plot))
# {
# curve_areas_means<-cbind(curve_areas_means, diff(apogee_transmission_readings_means_plot[,i])/diff(apogee_transmission_readings_means_plot_day[,1]))
# }

pca_plot_mean<-prcomp(apogee_transmission_readings_plot)


#par(mfrow=c(4,1))
# plots_for_plot_day<-sort(unique(unlist(strsplit(names(apogee_transmission_readings_means_plot_day)[grep(paste("_", plot_day, sep=""),names(apogee_transmission_readings_means_plot_day))], split = "_"))))[-1]

clr<-c("blue", "orange")
if(ncol(pca_plot_mean$x) >1) #if there was enough data to generate at least 2 PCs
{plot(pca_plot_mean$x[,1], pca_plot_mean$x[,2], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 1&2", genotype,"All Leaves per Plot Day", plot_day), xlab="PC1", ylab="PC2", pch=20)}
if(ncol(pca_plot_mean$x) >3) #if PC 3 and 4 are there
{plot(pca_plot_mean$x[,3], pca_plot_mean$x[,4], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 3&4", genotype,"All Leaves per Plot Day", plot_day), xlab="PC3", ylab="PC4", pch=20)}
#legend("bottomleft",legend=c("uninoc", "inoc"), col=c("orange", "blue"), pch=19)#colorbyinoculationstatus
}
}
```

clr<-c("blue", "orange")
if(ncol(pca_plot_mean$x) >1) #if there was enough data to generate at least 2 PCs
{plot(pca_plot_mean$x[,1], pca_plot_mean$x[,2], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 1&2", genotype,"All Leaves per Plot Day", plot_day), xlab="PC1", ylab="PC2", pch=20)}
if(ncol(pca_plot_mean$x) >3) #if PC 3 and 4 are there
{plot(pca_plot_mean$x[,3], pca_plot_mean$x[,4], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 3&4", genotype,"All Leaves per Plot Day", plot_day), xlab="PC3", ylab="PC4", pch=20)}
#legend("bottomleft",legend=c("uninoc", "inoc"), col=c("orange", "blue"), pch=19)#colorbyinoculationstatus
}
}
```

####MN1606
```{r rsmnt_pc_mn1606_trt, fig.align='center'}
apogee_transmission_readings<-apogee_transmission_readings_backup
genotype=unique(experiment_info$Genotype)[4] ##change the number for the genotype you want
#unique(experiment_info$Genotype) = Minnsoy Noir    McCall  MN1606  Ag2107 MN1410 
for (plot_day in sort(as.numeric(as.character(unique(experiment_info$PictureDay)))))
{

apogee_transmission_readings_plot<-as.data.frame(apogee_transmission_readings[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype == genotype),])
if  (nrow(apogee_transmission_readings_plot)>1){ #if there is more than 1 reading
# curve_areas_means<-NULL
# for(i in 1:ncol(apogee_transmission_readings_means_plot))
# {
# curve_areas_means<-cbind(curve_areas_means, diff(apogee_transmission_readings_means_plot[,i])/diff(apogee_transmission_readings_means_plot_day[,1]))
# }

pca_plot_mean<-prcomp(apogee_transmission_readings_plot)


#par(mfrow=c(4,1))
# plots_for_plot_day<-sort(unique(unlist(strsplit(names(apogee_transmission_readings_means_plot_day)[grep(paste("_", plot_day, sep=""),names(apogee_transmission_readings_means_plot_day))], split = "_"))))[-1]

clr<-c("blue", "orange")
if(ncol(pca_plot_mean$x) >1) #if there was enough data to generate at least 2 PCs
{plot(pca_plot_mean$x[,1], pca_plot_mean$x[,2], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 1&2", genotype,"All Leaves per Plot Day", plot_day), xlab="PC1", ylab="PC2", pch=20)}
if(ncol(pca_plot_mean$x) >3) #if PC 3 and 4 are there
{plot(pca_plot_mean$x[,3], pca_plot_mean$x[,4], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 3&4", genotype,"All Leaves per Plot Day", plot_day), xlab="PC3", ylab="PC4", pch=20)}
#legend("bottomleft",legend=c("uninoc", "inoc"), col=c("orange", "blue"), pch=19)#colorbyinoculationstatus
}
}
```

####AG2107
```{r rsmnt_pc_ag2107_trt, fig.align='center'}
apogee_transmission_readings<-apogee_transmission_readings_backup
genotype=unique(experiment_info$Genotype)[5] ##change the number for the genotype you want
#unique(experiment_info$Genotype) = Minnsoy Noir    McCall  MN1606  Ag2107 MN1410 
for (plot_day in sort(as.numeric(as.character(unique(experiment_info$PictureDay)))))
{

apogee_transmission_readings_plot<-as.data.frame(apogee_transmission_readings[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype == genotype),])
if  (nrow(apogee_transmission_readings_plot)>1){ #if there is more than 1 reading
# curve_areas_means<-NULL
# for(i in 1:ncol(apogee_transmission_readings_means_plot))
# {
# curve_areas_means<-cbind(curve_areas_means, diff(apogee_transmission_readings_means_plot[,i])/diff(apogee_transmission_readings_means_plot_day[,1]))
# }

pca_plot_mean<-prcomp(apogee_transmission_readings_plot)


#par(mfrow=c(4,1))
# plots_for_plot_day<-sort(unique(unlist(strsplit(names(apogee_transmission_readings_means_plot_day)[grep(paste("_", plot_day, sep=""),names(apogee_transmission_readings_means_plot_day))], split = "_"))))[-1]

clr<-c("blue", "orange")
if(ncol(pca_plot_mean$x) >1) #if there was enough data to generate at least 2 PCs
{plot(pca_plot_mean$x[,1], pca_plot_mean$x[,2], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 1&2", genotype,"All Leaves per Plot Day", plot_day), xlab="PC1", ylab="PC2", pch=20)}
if(ncol(pca_plot_mean$x) >3) #if PC 3 and 4 are there
{plot(pca_plot_mean$x[,3], pca_plot_mean$x[,4], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 3&4", genotype,"All Leaves per Plot Day", plot_day), xlab="PC3", ylab="PC4", pch=20)}
#legend("bottomleft",legend=c("uninoc", "inoc"), col=c("orange", "blue"), pch=19)#colorbyinoculationstatus
}
}
```


####MN1410
```{r rsmnt_pc_mn1410_trt, fig.align='center'}
apogee_transmission_readings<-apogee_transmission_readings_backup
genotype=unique(experiment_info$Genotype)[6] ##change the number for the genotype you want
#unique(experiment_info$Genotype) = Minnsoy Noir    McCall  MN1606  Ag2107 MN1410 
for (plot_day in sort(as.numeric(as.character(unique(experiment_info$PictureDay)))))
{

apogee_transmission_readings_plot<-as.data.frame(apogee_transmission_readings[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype == genotype),])
if  (nrow(apogee_transmission_readings_plot)>1){ #if there is more than 1 reading
# curve_areas_means<-NULL
# for(i in 1:ncol(apogee_transmission_readings_means_plot))
# {
# curve_areas_means<-cbind(curve_areas_means, diff(apogee_transmission_readings_means_plot[,i])/diff(apogee_transmission_readings_means_plot_day[,1]))
# }

pca_plot_mean<-prcomp(apogee_transmission_readings_plot)


#par(mfrow=c(4,1))
# plots_for_plot_day<-sort(unique(unlist(strsplit(names(apogee_transmission_readings_means_plot_day)[grep(paste("_", plot_day, sep=""),names(apogee_transmission_readings_means_plot_day))], split = "_"))))[-1]

clr<-c("blue", "orange")
if(ncol(pca_plot_mean$x) >1) #if there was enough data to generate at least 2 PCs
{plot(pca_plot_mean$x[,1], pca_plot_mean$x[,2], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 1&2", genotype,"All Leaves per Plot Day", plot_day), xlab="PC1", ylab="PC2", pch=20)}
if(ncol(pca_plot_mean$x) >3) #if PC 3 and 4 are there
{plot(pca_plot_mean$x[,3], pca_plot_mean$x[,4], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 3&4", genotype,"All Leaves per Plot Day", plot_day), xlab="PC3", ylab="PC4", pch=20)}
#legend("bottomleft",legend=c("uninoc", "inoc"), col=c("orange", "blue"), pch=19)#colorbyinoculationstatus
}
}
```

###PCs Midleaf by inoculation status {.tabset}
PLOTS SHOW PC1xPC2 and PC3&PC4 FOR EACH DAY 

Uninoculated = Blue |  Inoculated= Orange


#### MINNSOY
```{r rsmnt_pc_mid_minnsoy_trt, fig.align='center'}
apogee_transmission_readings<-apogee_transmission_readings_backup[which(experiment_info_backup$Leaf=="C"),]
genotype=unique(experiment_info$Genotype)[1] ##change the number for the genotype you want
#unique(experiment_info$Genotype) = Minnsoy Noir    McCall  MN1606  Ag2107 MN1410 
experiment_info<-experiment_info_backup[which(experiment_info$Leaf=="C"),]

for (plot_day in sort(as.numeric(as.character(unique(experiment_info$PictureDay)))))
{

apogee_transmission_readings_plot<-as.data.frame(apogee_transmission_readings[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype == genotype),])
if  (nrow(apogee_transmission_readings_plot)>1){
# curve_areas_means<-NULL
# for(i in 1:ncol(apogee_transmission_readings_means_plot))
# {
# curve_areas_means<-cbind(curve_areas_means, diff(apogee_transmission_readings_means_plot[,i])/diff(apogee_transmission_readings_means_plot_day[,1]))
# }

pca_plot_mean<-prcomp(apogee_transmission_readings_plot)


#par(mfrow=c(4,1))
# plots_for_plot_day<-sort(unique(unlist(strsplit(names(apogee_transmission_readings_means_plot_day)[grep(paste("_", plot_day, sep=""),names(apogee_transmission_readings_means_plot_day))], split = "_"))))[-1]

clr<-c("blue", "orange")
if(ncol(pca_plot_mean$x) >1)
{plot(pca_plot_mean$x[,1], pca_plot_mean$x[,2], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 1&2", genotype,"Midleaf per Plot Day", plot_day), xlab="PC1", ylab="PC2", pch=20)}
if(ncol(pca_plot_mean$x) >3)
{plot(pca_plot_mean$x[,3], pca_plot_mean$x[,4], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 3&4", genotype,"Midleaf per Plot Day", plot_day), xlab="PC3", ylab="PC4", pch=20)}
#legend("bottomleft",legend=c("uninoc", "inoc"), col=c("orange", "blue"), pch=19)#colorbyinoculationstatus
}
}
experiment_info<-experiment_info_backup
```

#### Noir
```{r rsmnt_pc_mid_noir_trt, fig.align='center'}
apogee_transmission_readings<-apogee_transmission_readings_backup[which(experiment_info$Leaf=="C"),]
genotype=unique(experiment_info$Genotype)[2] ##change the number for the genotype you want
#unique(experiment_info$Genotype) = Minnsoy Noir    McCall  MN1606  Ag2107 MN1410 
experiment_info<-experiment_info_backup[which(experiment_info$Leaf=="C"),]

for (plot_day in sort(as.numeric(as.character(unique(experiment_info$PictureDay)))))
{

apogee_transmission_readings_plot<-as.data.frame(apogee_transmission_readings[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype == genotype),])
if  (nrow(apogee_transmission_readings_plot)>1){
# curve_areas_means<-NULL
# for(i in 1:ncol(apogee_transmission_readings_means_plot))
# {
# curve_areas_means<-cbind(curve_areas_means, diff(apogee_transmission_readings_means_plot[,i])/diff(apogee_transmission_readings_means_plot_day[,1]))
# }

pca_plot_mean<-prcomp(apogee_transmission_readings_plot)


#par(mfrow=c(4,1))
# plots_for_plot_day<-sort(unique(unlist(strsplit(names(apogee_transmission_readings_means_plot_day)[grep(paste("_", plot_day, sep=""),names(apogee_transmission_readings_means_plot_day))], split = "_"))))[-1]

clr<-c("blue", "orange")
if(ncol(pca_plot_mean$x) >1)
{plot(pca_plot_mean$x[,1], pca_plot_mean$x[,2], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 1&2", genotype,"Midleaf per Plot Day", plot_day), xlab="PC1", ylab="PC2", pch=20)}
if(ncol(pca_plot_mean$x) >3)
{plot(pca_plot_mean$x[,3], pca_plot_mean$x[,4], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 3&4", genotype,"Midleaf per Plot Day", plot_day), xlab="PC3", ylab="PC4", pch=20)}
#legend("bottomleft",legend=c("uninoc", "inoc"), col=c("orange", "blue"), pch=19)#colorbyinoculationstatus
}
}
experiment_info<-experiment_info_backup
```


#### MCCALL
```{r rsmnt_pc_mid_mccall_trt, fig.align='center'}
apogee_transmission_readings<-apogee_transmission_readings_backup[which(experiment_info$Leaf=="C"),]
genotype=unique(experiment_info$Genotype)[3] ##change the number for the genotype you want
#unique(experiment_info$Genotype) = Minnsoy Noir    McCall  MN1606  Ag2107 MN1410 
experiment_info<-experiment_info_backup[which(experiment_info$Leaf=="C"),]

for (plot_day in sort(as.numeric(as.character(unique(experiment_info$PictureDay)))))
{

apogee_transmission_readings_plot<-as.data.frame(apogee_transmission_readings[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype == genotype),])
if  (nrow(apogee_transmission_readings_plot)>1){
# curve_areas_means<-NULL
# for(i in 1:ncol(apogee_transmission_readings_means_plot))
# {
# curve_areas_means<-cbind(curve_areas_means, diff(apogee_transmission_readings_means_plot[,i])/diff(apogee_transmission_readings_means_plot_day[,1]))
# }

pca_plot_mean<-prcomp(apogee_transmission_readings_plot)


#par(mfrow=c(4,1))
# plots_for_plot_day<-sort(unique(unlist(strsplit(names(apogee_transmission_readings_means_plot_day)[grep(paste("_", plot_day, sep=""),names(apogee_transmission_readings_means_plot_day))], split = "_"))))[-1]

clr<-c("blue", "orange")
if(ncol(pca_plot_mean$x) >1)
{plot(pca_plot_mean$x[,1], pca_plot_mean$x[,2], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 1&2", genotype,"Midleaf per Plot Day", plot_day), xlab="PC1", ylab="PC2", pch=20)}
if(ncol(pca_plot_mean$x) >3)
{plot(pca_plot_mean$x[,3], pca_plot_mean$x[,4], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 3&4", genotype,"Midleaf per Plot Day", plot_day), xlab="PC3", ylab="PC4", pch=20)}
#legend("bottomleft",legend=c("uninoc", "inoc"), col=c("orange", "blue"), pch=19)#colorbyinoculationstatus
}
}
experiment_info<-experiment_info_backup
```


#### MN1606
```{r rsmnt_pc_mid_mn1606_trt, fig.align='center'}
apogee_transmission_readings<-apogee_transmission_readings_backup[which(experiment_info$Leaf=="C"),]
genotype=unique(experiment_info$Genotype)[4] ##change the number for the genotype you want
#unique(experiment_info$Genotype) = Minnsoy Noir    McCall  MN1606  Ag2107 MN1410 
experiment_info<-experiment_info_backup[which(experiment_info$Leaf=="C"),]

for (plot_day in sort(as.numeric(as.character(unique(experiment_info$PictureDay)))))
{

apogee_transmission_readings_plot<-as.data.frame(apogee_transmission_readings[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype == genotype),])
if  (nrow(apogee_transmission_readings_plot)>1){
# curve_areas_means<-NULL
# for(i in 1:ncol(apogee_transmission_readings_means_plot))
# {
# curve_areas_means<-cbind(curve_areas_means, diff(apogee_transmission_readings_means_plot[,i])/diff(apogee_transmission_readings_means_plot_day[,1]))
# }

pca_plot_mean<-prcomp(apogee_transmission_readings_plot)


#par(mfrow=c(4,1))
# plots_for_plot_day<-sort(unique(unlist(strsplit(names(apogee_transmission_readings_means_plot_day)[grep(paste("_", plot_day, sep=""),names(apogee_transmission_readings_means_plot_day))], split = "_"))))[-1]

clr<-c("blue", "orange")
if(ncol(pca_plot_mean$x) >1)
{plot(pca_plot_mean$x[,1], pca_plot_mean$x[,2], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 1&2", genotype,"Midleaf per Plot Day", plot_day), xlab="PC1", ylab="PC2", pch=20)}
if(ncol(pca_plot_mean$x) >3)
{plot(pca_plot_mean$x[,3], pca_plot_mean$x[,4], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 3&4", genotype,"Midleaf per Plot Day", plot_day), xlab="PC3", ylab="PC4", pch=20)}
#legend("bottomleft",legend=c("uninoc", "inoc"), col=c("orange", "blue"), pch=19)#colorbyinoculationstatus
}
}
experiment_info<-experiment_info_backup
```


#### AG2107
```{r rsmnt_pc_mid_ag2107_trt, fig.align='center'}
apogee_transmission_readings<-apogee_transmission_readings_backup[which(experiment_info$Leaf=="C"),]
genotype=unique(experiment_info$Genotype)[5] ##change the number for the genotype you want
#unique(experiment_info$Genotype) = Minnsoy Noir    McCall  MN1606  Ag2107 MN1410 
experiment_info<-experiment_info_backup[which(experiment_info$Leaf=="C"),]

for (plot_day in sort(as.numeric(as.character(unique(experiment_info$PictureDay)))))
{

apogee_transmission_readings_plot<-as.data.frame(apogee_transmission_readings[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype == genotype),])
if  (nrow(apogee_transmission_readings_plot)>1){
# curve_areas_means<-NULL
# for(i in 1:ncol(apogee_transmission_readings_means_plot))
# {
# curve_areas_means<-cbind(curve_areas_means, diff(apogee_transmission_readings_means_plot[,i])/diff(apogee_transmission_readings_means_plot_day[,1]))
# }

pca_plot_mean<-prcomp(apogee_transmission_readings_plot)


#par(mfrow=c(4,1))
# plots_for_plot_day<-sort(unique(unlist(strsplit(names(apogee_transmission_readings_means_plot_day)[grep(paste("_", plot_day, sep=""),names(apogee_transmission_readings_means_plot_day))], split = "_"))))[-1]

clr<-c("blue", "orange")
if(ncol(pca_plot_mean$x) >1)
{plot(pca_plot_mean$x[,1], pca_plot_mean$x[,2], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 1&2", genotype,"Midleaf per Plot Day", plot_day), xlab="PC1", ylab="PC2", pch=20)}
if(ncol(pca_plot_mean$x) >3)
{plot(pca_plot_mean$x[,3], pca_plot_mean$x[,4], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 3&4", genotype,"Midleaf per Plot Day", plot_day), xlab="PC3", ylab="PC4", pch=20)}
#legend("bottomleft",legend=c("uninoc", "inoc"), col=c("orange", "blue"), pch=19)#colorbyinoculationstatus
}
}
experiment_info<-experiment_info_backup
```


#### MN1410
```{r rsmnt_pc_mid_mn1410_trt, fig.align='center'}
apogee_transmission_readings<-apogee_transmission_readings_backup[which(experiment_info$Leaf=="C"),]
genotype=unique(experiment_info$Genotype)[6] ##change the number for the genotype you want
#unique(experiment_info$Genotype) = Minnsoy Noir    McCall  MN1606  Ag2107 MN1410 
experiment_info<-experiment_info_backup[which(experiment_info$Leaf=="C"),]

for (plot_day in sort(as.numeric(as.character(unique(experiment_info$PictureDay)))))
{

apogee_transmission_readings_plot<-as.data.frame(apogee_transmission_readings[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype == genotype),])
if  (nrow(apogee_transmission_readings_plot)>1){
# curve_areas_means<-NULL
# for(i in 1:ncol(apogee_transmission_readings_means_plot))
# {
# curve_areas_means<-cbind(curve_areas_means, diff(apogee_transmission_readings_means_plot[,i])/diff(apogee_transmission_readings_means_plot_day[,1]))
# }

pca_plot_mean<-prcomp(apogee_transmission_readings_plot)


#par(mfrow=c(4,1))
# plots_for_plot_day<-sort(unique(unlist(strsplit(names(apogee_transmission_readings_means_plot_day)[grep(paste("_", plot_day, sep=""),names(apogee_transmission_readings_means_plot_day))], split = "_"))))[-1]

clr<-c("blue", "orange")
if(ncol(pca_plot_mean$x) >1)
{plot(pca_plot_mean$x[,1], pca_plot_mean$x[,2], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 1&2", genotype,"Midleaf per Plot Day", plot_day), xlab="PC1", ylab="PC2", pch=20)}
if(ncol(pca_plot_mean$x) >3)
{plot(pca_plot_mean$x[,3], pca_plot_mean$x[,4], col=clr[as.numeric(experiment_info$Treatment[which(experiment_info$PictureDay==plot_day & experiment_info$Genotype ==genotype)])], main=paste("PC 3&4", genotype,"Midleaf per Plot Day", plot_day), xlab="PC3", ylab="PC4", pch=20)}
#legend("bottomleft",legend=c("uninoc", "inoc"), col=c("orange", "blue"), pch=19)#colorbyinoculationstatus
}
}
experiment_info<-experiment_info_backup
```
